Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-16 Manuscript/proof_outline.tex
explain product space notation

{\color{blue}In contrast to statements already part of
  \leanline{mathlib}, in the sequel we \leanlinecolor{highlight}
  definitions and statements which are part of our own code.} In the
formalization of the above, we use \leanline{variable {ι : Type _} {α
    : ι → Type _} }, which fixes the index set $\iota$ and all spaces
$\alpha_t, t\in\iota$ as global variables. In addition, note that the
projective property we use here works as long as we have a preorder
(which is the subset relation on \leanline{Finset ι} below).

@@

\noindent
With this, we can define the projetive family as follows. The typeclass inference system of
\leanline{Lean} automatically uses the subset relation to generate
\leanline{[Preorder (Finset ι)]} when \leanline{isProjective} is
called.

>>>>

In contrast to statements already part of
\leanline{mathlib}, in the sequel we \leanlinecolor{highlight}
definitions and statements which are part of our own code. In the
formalization of the above, we use \leanline{variable {ι : Type _} {α: ι → Type _}},
which fixes the index set $\iota$ and all spaces
$\alpha_t, t\in\iota$ as global variables.
In Lean, the product space is then \leanline{∀ j : ι, α j} and the product over a finite set \leanline{J} is \leanline{∀ j : J, α j}.

We formalize the projective property as follows. This definition is not specific to measures but works as long as we have a preorder
(which is the subset relation on \leanline{Finset ι} below).

@@

\noindent
With this, we can define the projective family as follows. The typeclass inference system of
\leanline{Lean} automatically uses the subset relation to generate
\leanline{[Preorder (Finset ι)]} when \leanline{isProjective} is
called.
